---
title: "My first analysis: A report"
author: Mark Andrews
date: "Monday, June 27, 2020"
output:
  pdf_document:
    keep_tex: true
    toc: true
header-includes:
  - \usepackage{booktabs}
bibliography: refs.bib
biblio-style: apalike
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo=FALSE)
```

```{r libraries, echo=F}
library(tidyverse)
library(knitr)
library(kableExtra)
library(pander)
set.seed(101010)
```

# Introduction

This **is my introduction**.

## Hypothesis

This *is my hypothesis*.

### Main hypothesis

The \underline{main hypothesis} is ...

```{r my_figure, fig.cap='My scatterplot. It is nice.', out.width="0.67\\textwidth", fig.align='center'}
data_df <- tibble(x = rnorm(10),
                  y = rnorm(10))
ggplot(data_df,
       aes(x = x, y = y)) + geom_point() + theme_classic()
```


```{r}
# data_summary <- data_df %>%
#   summarise_all(list(mean = mean, sd = sd)) %>%
#   rename_all(~str_replace_all(., '_', ''))

data_summary <- select(diamonds, color, clarity, depth, price) %>% slice(1:10)

make_table <- function(data){
  kable(data,
        format = "latex",
        digits = 2,
        booktabs = TRUE) %>% 
    kable_styling(position = 'center')
}

make_table(data_summary)
```


```{r, comment='>', fig.cap='foo'}
M <- lm(y ~ x, data = data_df)
S <- summary(M)

make_table(S$coefficients)
```

From this analysis, $R^2 = `r round(S$r.squared, 2)`$.

Here is a [link](http://www.nytimes.com).

As was shown by @kantz:2004nonlinear that nonlinear analysis is hard.
It is known that nonlinear time series is hard [@kantz:2004nonlinear;@das1994time].
See also @stone:aic, page 45.


```{r, eval=FALSE, echo=TRUE}
M <- brm(y ~ x, data = data_df)
```

# A list of things

* Blue
* Red
* Green

## More colours

1. Blue
    1. Light blue
    1. Navy blue
    1. Baby blue
1. Green 
    * Forest green 
    * Dark green

# Numbered list

5. Blue
8. Red
3. Green
89. Purple
17. Orange

# The statistical model

Our model is 
$$
y_i \leq \alpha + \beta x_i + \epsilon_i
$$

We use \LaTeX.

# A definition list 

height
: The person's height in cm

weight
: The person's weight in kg

age
: The person's age in years

# Bibliography